---
title: "CIS 351 B: Week 3 Lecture 1"
author: "Your Name"
format: 
  html:
    embed-resources: true
---

## Data Types in R

In this course, we will work with the following three data types:

1. **Numeric:** numbers, e.g., `13`, `pi`, `5e-5`.

2. **Characters:** texts that are *not* numbers, they can letters or words combined with numbers and/or symbols. Examples of characters in R are: `"Flagler"`, `"Henry Flagler"`, `"AX14_BY77"`.

3. **Logical (Boolean):** binary values corresponding to `TRUE` and `FALSE`. 

We use the function `class()` to determine the data type of an object.

### Numeric Values

```{r}
class(13)
```

```{r}
class(pi^3/2)
```

```{r}
class(5e-5)
```

```{r}
x <- sqrt(pi^3)

class(x)
```

### Character Values

```{r}
class("Pacific Ocean")
```

```{r}
class("13")
```

```{r}
fruits <- c("apple", "orange", "banana", "strawberry")

class(fruits)
```

::: {.callout-caution}
Character values in R are always wrapped by quotation marks.
:::

### Logical Values

```{r}
TRUE

FALSE
```

```{r}
class(TRUE)

class(FALSE)
```

```{r}
3 > pi
```

```{r}
1 == 2 # is 1 equal to 2?
```

```{r}
# is cos(pi/2) less than or equal 0?
cos(pi/2) <= 0
# cos(pi/2) in R is a small, but positive number, thus cos(pi/2) <= 0 in R is a false statement
```

```{r}
fruits[1] == 'apple'
```

```{r}
fruits[1] == 'orange'
```

::: {.callout-note}
In R, we use `==` to check for equality of two objects. And `!=` to check whether two objects are not equal to each other. 

In most modern programming languages (R included), `!` is used to negate a statement.
:::

**Exercise 1.** Is the 2nd item in `fruits` not equal to `kiwi`?

```{r}
fruits[2] != 'kiwi'
```

```{r}
!(fruits[1] == 'apple')
```